Demes: a standard format for demographic models

### 2022-08-26 paper.tex
Addresses and fix affil ordering

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Gertjan Bisschop}
\author[4]{Ryan N. Gutenkunst}
\author[3]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[8]{Stephan Schiffels}
\author[4]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\ddagger$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[4]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California, Irvine}
\affil[8]{Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

>>>>

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Gertjan Bisschop}
\author[4]{Ryan N. Gutenkunst}
\author[3]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[6]{Stephan Schiffels}
\author[4]{Travis J. Struck}
%Senior Authors
\author[7,$\dagger$,$\ddagger$]{Jerome Kelleher}
\author[8,$\dagger$]{Kevin R. Thornton}
\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen, 1350 Copenhagen K, Denmark}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison, WI 53706, USA}
\affil[3]{Institute of Ecology and Evolution, The University of Edinburgh, EH9 3FL, UK}
\affil[4]{Department of Molecular and Cellular Biology, University of Arizona, Tucson, AZ 85721, USA}
\affil[5]{Computer Technologies Laboratory, ITMO University, 197101, Saint-Petersburg, Russia}
\affil[6]{Max Planck Institute for Evolutionary Anthropology, 04103 Leipzig, Germany}
\affil[7]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, OX3 7LF, UK}
\affil[8]{Ecology and Evolutionary Biology, University of California, Irvine, CA 92697, USA}
